\documentclass[10pt,sans,letterpaper]{moderncv}

\usepackage[margin=0.5in]{geometry}

\moderncvstyle{classic}
\moderncvcolor{orange}
\moderncvicons{awesome}

\setlength{\hintscolumnwidth}{1in}

\name{Denton}{Liu}
\title{Software Engineering}
\phone{(647) 739-9932}
\email{denton.liu@uwaterloo.ca}
\homepage{dentonliu.me}
\social[linkedin]{DentonL}
\social[github]{Denton-L}

\begin{document}
\makecvtitle

\section{Summary of Qualifications}
\cvlistitem{Proficient in Java, C, C++ and various assembly languages.}
\cvlistitem{Enjoys working in and understanding low-level environments such as embedded systems.}
\cvlistitem{Familiar with building websites using HTML5, CSS3 and JavaScript.}
\cvlistitem{Adept with Linux and common applications such as Git and GDB.}

\section{Projects}
\cvitem{LAByrinth}{
	\begin{itemize}
		\item{Created a labyrinth game using an Arduino-like microcontroller with C.}
		\item{Utilised both serial and parallel I/O to communicate with peripherals.}
		\item{Wrote an abstraction layer over hardware in order simplify higher-level development.}
	\end{itemize}
}\vspace{-0.5\baselineskip}
\cvitem{Breadboard Computer}{
	\begin{itemize}
		\item{Created a computer based on the 6502 processor on a breadboard using only ICs (integrated circuits).}
		\item{Programmed a version of Pong using 6502 assembly.}
		\item{Utilised an EEPROM programmer to load an assembled hex image.}
	\end{itemize}
}\vspace{-0.5\baselineskip}
\cvitem{Java-Webchat}{
	\begin{itemize}
		\item{Employed RMI (Remote Method Invocation) to communicate between server and clients.}
		\item{Implemented a user database which took precautions to secure user data using salted hashes.}
		\item{Made use of object-oriented programming principles in order to create a cleaner codebase.}
	\end{itemize}
}\vspace{-\baselineskip}

\section{Experience}
\cventry{2014}{IT Volunteer}{Administration}{Newcomer Centre of Peel}{}{
	\begin{itemize}
		\item{Created tool to backup user data using Windows Batch scripting.}
		\item{Acted as system administrator.}
		\item{Provided technical assistance to employees.}
	\end{itemize}
}
\cventry{2010--2015}{Cadet Warrant Officer}{Royal Canadian Air Cadets}{700 David Hornell VC Squadron}{}{
	\begin{itemize}
		\item{Planned and organised events, such as training weekends, as a member of a team.}
		\item{Captained the drill team consisting of the squadron's most successful cadets.}
		\item{Commanded over 120 peers during graduation parade of Drill and Ceremonial Instructors Course.}
	\end{itemize}
}

\section{Education}
\cventry{2015--2020}{Candidate for Bachelors of Software Engineering}{University of Waterloo}{Waterloo, Ontario}{}{
	\textit{Cumulative GPA}: 3.85 
}
\cventry{2011--2015}{Ontario Secondary School Diploma}{Martingrove Collegiate Institute}{Toronto, Ontario}{}{
	\textit{Academic Average}: 95.0\%
}

\section{Awards and Scholarships}
\cvitemwithcomment{2015}{Sandford Fleming Foundation Programming Competition Award}{Second Place}
\cvitemwithcomment{2015}{Dean's Honours List at University of Waterloo}{Term Average of 87\% or Greater}
\cvitemwithcomment{2014}{University of Toronto High School Design Competition}{First Place}

\section{Interests and Hobbies}
\cvlistitem{Plays cello, double bass and piano.}
\cvlistitem{Avid unicyclist.}
\cvlistitem{Fanatical user of \LaTeX.}
\cvlistitem{Proud Vim user.}
\cvlistitem{Runs Arch Linux on personal computer.}

\end{document}
